Precious Metals Or Crypto, Where Should I Invest?

### 2024-04-18 paper/paper.qmd
Finished Paper

__________
Then the average true range was calculated with and represented by (asset)_ATR in @tbl-3:

@@

__________
In the final step, the normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @tbl-3:

@@

### Model Justification
I expect there to be a positive correlation between

# Results
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <- readRDS(file = here::here("models/volatility chart.rds"))

@@

@@

Our results are summarized in...

```{r}
#| echo: false
#| warning: false
#| label: fig-3s
#| fig-cap: "Volatility Chart"

first_model
```
The Volatility chart shows that

@@

## Cryptocurrencies As An Investment
Cryptocurrencies is the new wave. Aside from Bitcoin and Ethereum, we are have seen the rise of many other successful cryptocurrencies such as Monero, Litecoin, and Stellar Lumens just to name a few. @fig-1 can attest to the substantial growth of cryptocurrencies over the last decade. However, @fig-2 shows that even though Bitcoin and Ethereum has been extremely profitable, they are both extremely volatile assets with normalized average true range values over 5 times that of precious metals. As an investor, cryptocurrencies can be much more appealing, especially towards the newer crowd. Investing in crypto is much more straightforward than precious metals. With large crypto exchanges such as Coinbase, Binance, and Kraken gaining popularity buying crypto has never been easier. Moreover, crypto wallets can come in the form of a USB Ledger or even an app on the appstore. This makes the asset extremely lightweight and mobile.

## Different Stroke For Different Folks
Both cryptocurrencies and precious metals are amazing investments.Throughout my analysis, I have concluded that there is a correlation between the two category of assets, both assets have seen massive growth, and both still have a lot of room to develop in the future. For the readers still asking: Which asset should I invest in? I believe the answer is this:

@@

For those who are looking for something long or short term, and that are more risk-seeking, cryptocurrencies will be your cup of tea. Though seemingly much more profitable in the recent years, these assets are much more volatile and is very dependent on economic climate. Moreover, compared to precious metals, buying, storing, and selling is a breeze. In cryptocurrencies is an asset with very high potential ceiling and as blockchain technology continues to progress, cryptocurrencies have a very bright future.

## Biases and Weaknesses
One of the greatest weaknesses stems from the limited historical data of cryptocurrencies. The value of precious metals can be trace back centuries and has solidified itself as a solid holding asset while cryptocurrencies such as Ethereum was only introduced in the late 2016s. Therefore, the only results and conclusion that can be made...

## Next Steps
Some next steps I can take for future developments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic conditions and how that compares to precious metals.

## Closing Remarks
Before investing in anything, nothing beats your own research. An investment should be considered only after sufficient self evaluation. Ask yourself:

@@

I have given but a brief overview an analyses of two popular modern day assets. The rest is up for you to discover.

>>>>

__________
Then the average true range was calculated with and represented by (asset)_ATR in @fig-1:

@@

__________
In the final step, the normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @fig-1:

@@

## Model Justification
Both precious metals and cryptocurrencies have been used historically as a way to hedge against inflation, so when the economy doesn't do well, investors look to buy up these assets as a way to preserve the value of their cash. Furthermore, these assets follow a similar integrity where they are mined, either digitally or physically, and there is a decreasing supply it the more they are mined. Considering all factors aforementioned, a linear regression model is a reasonable framework for assessing the relationship between the two assets.

{{< pagebreak >}}
# Results
```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false

library(rstanarm)
crypto$totalc <- crypto$eth_Close + crypto$btc_Close
metals$totalm <- metals$gold_Close + metals$silver_Close
price_join <- merge(crypto, metals, by = "Date", all = FALSE)
price_join <- select(price_join, Date, totalc, totalm)
first_model <- readRDS(file = here::here("models/volatility chart.rds"))
esfit <- stan_glm(
  formula = totalc ~ totalm,
  data = price_join,
  family = gaussian()
)

reg <- ggplot(price_join, aes(x = totalm, y = totalc)) +
  geom_point(color = "blue", size = 2) +
  geom_abline(intercept = coef(esfit)[1], slope = coef(esfit)[2], color = "red") +
  labs(title = "Crypto vs. Metals Prices Regression Model",
       x = "Metals Closing Price", y = "Cryptos Closing Price")

@@

```{r}
#| label: fig-2
#| fig-cap: "Model showing relationship between metals prices and crypto prices"
#| echo: false
#| warning: false

reg
```

@fig-2 suggests that the prices of aggregated metals (gold and silver) and that of aggregated cryptos (Bitcoin and Ethereum) have a positive and strong relationship. This is reinforced when observing the summary data below. There is a positive coefficient at 1.6 for totalm (aggregated metals). In other words, as the price of the aggregated metals increase by 1 unit, the model predicts an increase in aggregated crypto by 1.6 units on average. The correlation analysis concludes an r value of ~0.71. The aforementioned information suggest a moderately strong and positive relationship between precious metals aggregate price and crypto aggregate prices. Though there is a positive correlation between the price factors of these asset categories, there is no implication of causation.

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Summary Data for Regression Model"

esfit
"__________________________"
"Correlation:"
correlation <- cor(price_join$totalm, price_join$totalc)
correlation
```

@@

The volatility results strongly suggests that cryptocurrencies are much more unstable compared to precious metals. I use normalized average true range as a measure because it takes the average range between high and low prices over a specific period. Higher ATR values suggest higher volatility because there is a greater shift in prices. The normalized ATR is the ATR normalized over the closing price of that day as a way to balance and fairly judge the ATR of the four individual assets. @fig-3 shows evidently that the normal ATR values of Bitcoin and Ethereum dwarfs those of gold and silver. Gold is the most consistent with a normalized ATR resting consistently at 0.01, silver is the second most stable coming in at around 0.02. The two cryptocurrencies see way higher normalized ATR values I would estimate to be around 0.05 on average and a much more turbulent trend line. This data is congruent with our price chart @fig-1 where gold had the most stable price rise followed by silver and then the cryptos. Because the normalized ATR for the cryptocurrencies are many times higher than that of precious metals, we can assume that they are also significantly more volatile.

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "Volatility Chart Observed Through Normalized Average True Range"

first_model
```

@@

## Cryptocurrencies As An Investment
Cryptocurrencies is the new wave. Aside from Bitcoin and Ethereum, we are have seen the rise of many other successful cryptocurrencies such as Monero, Litecoin, and Stellar Lumens just to name a few. @fig-1 can attest to the substantial growth of cryptocurrencies over the last decade: Bitcoin grew from 7,000 USD to almost 70,000 USD in the span of less than 7 years. Ethereum grew from around 330 USD to over 3500 USD. 10x of an investment over less than 7 years is sensationally high retruns. However, @fig-3 shows that even though Bitcoin and Ethereum has been extremely profitable, they are both extremely volatile assets with normalized average true range values many times that of precious metals. Due to the extreme volatility of cryptos, many begin looking at crypto as assets for day trading or short term options. As an investor, cryptocurrencies can be much more appealing, especially towards the newer crowd because investing in crypto is much more straightforward than precious metals. With large crypto exchanges such as Coinbase, Binance, and Kraken gaining popularity buying crypto has never been easier. Moreover, crypto wallets can come in the form of a USB Ledger or even an app on the appstore. This makes the asset extremely lightweight and mobile.

## Different Stroke For Different Folks
Both cryptocurrencies and precious metals are amazing investments.Throughout my analysis, I have concluded that there is a strong positive relationship between the two category of assets, both assets have seen massive growth, and both still have a lot of room to develop in the future. For the readers still asking: Which asset should I invest in? I believe the answer is this:

@@

For those who are looking for something long or short term, and that are more risk-seeking, cryptocurrencies will be your cup of tea. Though seemingly much more profitable in the recent years, these assets are much more volatile and is very dependent on economic climate. Movements such as currencies being delisted from major exchanges or countries enforcing crypto laws can result in massive movements and potentially even the downfall of a cryptocurrency. This potentially tumultuous investment will take significantly more effort when it comes to monitoring activity and making adjustments. However, compared to precious metals, buying, storing, and selling is a breeze. Cryptocurrencies are assets with a very high potential ceiling and as blockchain technology continues to progress, cryptocurrencies have a very bright future.

## Biases and Weaknesses
The potential bias in my analysis comes from data recording errors from yahoo finance. However, that should be pretty minimal. Another potential bias could result from selection bias that occurs in my data cleaning. I chose to only take the first and fifteenth day of every month when creating my price charts and Normal ATR charts. Though said selection process can help reduce noise and ignore short term variations, I could very well have missed out on certain trends that occur on the days between. Aside from data biases, one incorrect assumption could be that the relationship between crypto and precious metals is linear. In many instances from the price chart @fig-1, there seem to be exponential growth from crypto compared to linear grown from metals and this is observed again in @fig-2 where there is a slight curve in the points suggesting potential a exponential regression model.

One of the greatest weaknesses in my analysis stems from the limited historical data of cryptocurrencies. The value of precious metals can be trace back a century ago and has solidified itself as a strong holding asset while cryptocurrencies such as Ethereum was only introduced in the late 2017s. As a relatively immature market paired with easy influence from outside factors such as technological advancements and crypto laws, there are too many qualitative aspects that need to be accounted for but my analysis can only give a quantitative prediction based on historical prices.

## Next Steps
Some next steps I can take for future developments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic patterns and how that compares to precious metals. Moreover, I can include more assets in my comparisons such as technology stocks or real estate. The overall next step for improving this analysis is to increase the amount of factors

## Closing Remarks
Before investing in anything, nothing beats individual research. An investment should be considered only after sufficient self evaluations.

Ask yourself:

@@

I have given but a brief overview and analyses of two popular modern day assets. The rest is up for you to discover.
